Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-25 paper/snakemajoranas.tex
Majorana decay length -> Majorana size, everywhere

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/bandstructures}
\caption{Band stuctures of the system in Fig.~\ref{fig:setup}(b) with different zigzag amplitudes.
The blue lines correspond to a trivial phase ($\phi=0$, $B=0$) and the orange lines to a topological phase ($\phi=\pi$, $B = \SI{1}{T}$).
The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=W/2$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
On the $x$-axis is the Bloch momentum where $z_x=\SI{1300}{\nm}$.
Subplot (a) has a different scale on the $x$-axis for $k_x < 0$ than the other subplots and displays the unfolded band structure.
For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=dE/dk$ can be compared visually.
We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes insensitive to the momentum $k_x$ and equivalently, $v_\textrm{F}$ decreases.
As the zigzag amplitude increases, the band gap $E_\textrm{gap}$ increases by an order of magnitude.
The combination of these ensures a significant decrease of the Majorana decay length because $\xi_M \propto v_\textrm{F}/E_\textrm{gap}$
The parameter values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
\end{figure}

@@

\comment{We calculate the wave functions and find the Majorana lengths by fitting an exponential.}
We model a finite system to compute the Majorana wave function density for different geometries; ribbon, saw-toothed zigzag, parallel curves, and a variant of the latter with disordered edges.
In figure~\ref{fig:wave_functions} the wave functions are displayed, superimposed upon their respective geometry.
By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$, and by using the corresponding eigenstate of that lowest energy, we get the wave function.
To determine $\xi_\textrm{M}$, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum, then the fit to $\exp{x / \xi_\textrm{M}}$ becomes more robust.
Using this system, we then find the Majorana decay length $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
All systems have identical Hamiltonian parameters to compare the effects of the changing geometry meaningfully.

\comment{In a straight system, the Majoranas are very poorly localized.}
For the ribbon system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
The wave function extends to the center of the system, resulting in highly overlapping Majoranas and a non-zero energy of the state.
Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is high in comparison with the topological gap $E_\textrm{gap}$.
Altogether, the small topological gap, but also the before mentioned high velocity, result in poorly localized Majoranas and minimal topological protection against perturbations.  % TODO: probably put the eq for coherence length here?

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
We observe that for zigzag systems the Majorana properties improve.
All of the zigzag type geometries display a reduced coherence length, and the delocalized nature of the wave functions is improved, as is visible through the density plots.
Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the topological gap.
As mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar v_\textrm{F} / \Delta_\textrm{ind}$.
Additionally, the reduction of the Majorana decay length allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.

@@

\comment{Disorder has a similar effect, but one has no control over it.}
Recently, it has been shown~\cite{haim_double-edge_2018} that having a system with weak disorder can lead to a reduction in the Majorana decay length, similar to what happens with the introduction of a zigzag geometry.
However, in contrast to introducing weak disorder into a system, changing the geometry is experimentally much easier to realize and therefore easier to control.

>>>>

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/bandstructures}
\caption{Band stuctures of the system in Fig.~\ref{fig:setup}(b) with different zigzag amplitudes.
The blue lines correspond to a trivial phase ($\phi=0$, $B=0$) and the orange lines to a topological phase ($\phi=\pi$, $B = \SI{1}{T}$).
The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=W/2$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
On the $x$-axis is the Bloch momentum where $z_x=\SI{1300}{\nm}$.
Subplot (a) has a different scale on the $x$-axis for $k_x < 0$ than the other subplots and displays the unfolded band structure.
For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=dE/dk$ can be compared visually.
We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes insensitive to the momentum $k_x$ and equivalently, $v_\textrm{F}$ decreases.
As the zigzag amplitude increases, the band gap $E_\textrm{gap}$ increases by an order of magnitude.
The combination of these ensures a significant decrease of the Majorana size because $\xi_M \propto v_\textrm{F}/E_\textrm{gap}$
The parameter values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
\end{figure}

@@

\comment{We calculate the wave functions and find the Majorana lengths by fitting an exponential.}
We model a finite system to compute the Majorana wave function density for different geometries; ribbon, saw-toothed zigzag, parallel curves, and a variant of the latter with disordered edges.
In figure~\ref{fig:wave_functions} the wave functions are displayed, superimposed upon their respective geometry.
By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$, and by using the corresponding eigenstate of that lowest energy, we get the wave function.
To determine $\xi_\textrm{M}$, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum.
Using this system, we then find the Majorana size $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
All systems have identical Hamiltonian parameters to compare the effects of the changing geometry meaningfully.

\comment{In a straight system, the Majoranas are very poorly localized.}
For the straight system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
The wave function extends to the center of the system, resulting in highly overlapping Majoranas and a non-zero energy of the state.
Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is high in comparison with the topological gap $E_\textrm{gap}$.
Altogether, the small topological gap, but also the before mentioned high velocity, result in poorly localized Majoranas and minimal topological protection against perturbations.  % TODO: probably put the eq for coherence length here?

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
We observe that for zigzag systems the Majorana properties improve.
All of the zigzag type geometries display a reduced coherence length, and the delocalized nature of the wave functions is improved, as is visible through the density plots.
Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the topological gap.
As mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar v_\textrm{F} / \Delta_\textrm{ind}$.
Additionally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.

@@

\comment{Disorder has a similar effect, but one has no control over it.}
Recently, it has been shown~\cite{haim_double-edge_2018} that having a system with weak disorder can lead to a reduction in the Majorana size, similar to what happens with the introduction of a zigzag geometry.
However, in contrast to introducing weak disorder into a system, changing the geometry is experimentally much easier to realize and therefore easier to control.
